Supporting information

### 2023-10-31 paper/supplementary.qmd

>>>>

## Computation

We conducted adaptive Hamiltonian Monte Carlo sampling for the full and missing-
-data datasets. For the full dataset we obtained 1000 post-warmup samples each
from 4 independent Markov chains after 1000 warm-up samples and "hot-starting"
with a mass metric output by a previous model run.

For the missing-data dataset XXX.

# Laplace approximation case study

To compare MCMC sampling with Laplace approximation we used a different model.
 The full Maud input folders can be found at <https://github.com/biosustain/Methionine_model/tree/main/data/example_ode> 
and <https://github.com/biosustain/Methionine_model/tree/main/data/example_ode_laplace>

To generate Laplace samples we used Maud's Laplace mode.
